---
title: "problemSet_2.R"
output:
  pdf_document: default
  html_document: default
date: "2022-09-26"
---
myName <- "JingJianGao"

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Problem 1a-Analysis on Fuel Economy

```{r}
library(ggplot2)
vehicles <- read.csv("/Users/billg/Documents/vehicles.csv")
Regvehicle <- glm(comb08~fuelType1,data=vehicles)
ggplot <- ggplot(vehicles)
ggplot+aes(fuelType1,comb08)+
  geom_point(size=0.5)+xlab("fuelType1")+ylab("combined mpg for fuelType1")+
  ggtitle("fuelType1 vs combined mpg plot")

#This plot is showing the variety of fuels in fuelType1 and their relationship with combined mpg. 
#We can see the difference between different kinds of fuel and their MPG performance.

```

##Problem #1b-Analysis on Vehicle makers


```{r}
Regmaker <- glm(comb08~make,data=vehicles)
ggplot+aes(make,comb08)+geom_point(size=0.1)+xlab("Makers")+
  ylab("combined mpg for different vehicles")+
  ggtitle("Makers' Vehicles vs combined mpg plot")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(text = element_text(size = 5))

#This plot is about the relationship between combined miles per gallon and the 
#variety of vehicles made from different makers. 
#We can see the difference in performance of mpg among makers to know who made the most progress.


Regmaker2 <- glm(co2TailpipeGpm~make,data=vehicles)
ggplot+aes(make,co2TailpipeGpm)+geom_point(size=0.1)+xlab("Makers")+
  ylab("TailPipe CO2 emission from different vehicles")+
  ggtitle("Makers' Vehicles vs CO2 emission plot")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(text = element_text(size = 5))

#This plot is about the relationship between CO2 emission and 
#the variety of vehicles made from different makers. 
#We can see how much CO2 is produced by cars from certain makers to know how much progress 
#they made on reducing CO2 emission.




```
##Problem #2-Nasdaq

```{r}
library(tidyverse)
library(tidyquant)
library(scales)
nasdaq <- read.csv("/Users/billg/Downloads/IXIC21-22.csv")
ggplot <- ggplot(nasdaq)
ggplot+aes(x=as.Date(Date),y= Adj.Close)+geom_candlestick(aes(open=Open,high=High,low=Low,close=Close))+
  labs(title="Nasdaq Data Chart",y="AdjustClose",x="Date")+
  theme_tq()+scale_x_date(date_breaks = "2 months", date_labels = "%b%y")

#This candlestick plot shows the Nasdaq Stock Market's open, high, low, and close price 
#from 2021-9-21 to 2022-9-20


```
##Problem #3a-Rural capacity index

```{r}
ruralcapacity <- read.csv("/Users/billg/Downloads/ruralCapacityData.csv")
ggplot <- ggplot(ruralcapacity)
ggplot+(aes(num_fam,cap_index))+geom_point()+xlab("Number of Families")+
  ylab("The Rural Capacity Index")+
  ggtitle("Rural Capacity Index chart featuring number of families")

#The number of families doesn't affect the Rural Capacity Index a lot. 
#The number of families has few contributions to the Index
```
##Problem #3b

```{r}
ggplot+(aes(house_broadband,per_over_25_with_bach))+geom_point()+
  xlab("Total Households with Broadband connection")+
  ylab("Percent of population 25 and over with a bachelors degree")+
  ggtitle("Houses with broadband vs The percent of adults above 25 with bachelor degrees")

#This plot shows that there is not a strong correlation between 
#the total households with Broadband connection and the percentage of population. 
#But together, they have good impacts on the Capacity Index.

```

##Problem #3c

```{r}
ggplot+(aes(pop_total,cap_index))+geom_point()+xlab("Total Population")+
  ylab("The Rural Capacity Index")+
  ggtitle("Rural Capacity Index chart featuring Total Population")+xlim(0,16000)

#This plot shows the relationship between total population and Capacity index for 
#total population <16000

ggplot+(aes(pop_total,cap_index))+geom_point()+xlab("Total Population")+
  ylab("The Rural Capacity Index")+
  ggtitle("Rural Capacity Index chart featuring Total Population")+xlim(16000,55000)

#This plot shows the relationship between total population and Capacity index for 
#16000< total population <55000


ggplot+(aes(pop_total,cap_index))+geom_point()+xlab("Total Population")+
  ylab("The Rural Capacity Index")+
  ggtitle("Rural Capacity Index chart featuring Total Population")+xlim(55000,300000)

#This plot shows the relationship between total population and Capacity index for 
#total population >55000

```
#The Rural capacity Index seems to have a linear relationship with total population in graph 1

#The Rural capacity Index seems to maintain stable once the total population is 
#greater than 16000 as shown in graph 2

#The Rural capacity Index is greater than 80 for all total populations greater than 55000


